\documentclass[11pt]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage[default]{raleway}
\usepackage{multicol}

% Colors
\definecolor{accent}{RGB}{10,60,90}
\definecolor{secondary}{RGB}{30,30,30}

% Font settings
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\mytitle}[1]{\color{accent}\normalfont\large\bfseries{#1}}

% Section formatting
\titleformat{\section}{\mytitle}{}{0em}{}[{\titlerule[0.8pt]}]
\titlespacing{\section}{0pt}{12pt}{8pt}

% Itemize styling
\setlist[itemize]{leftmargin=*,nosep,after=\vspace{4pt}}
\setlist[itemize]{label=\color{accent}\scriptsize\raisebox{0.4ex}{\textbullet}}

% Custom commands
\newcommand{\tech}[1]{\textcolor{secondary}{\textbf{#1}}}

\newcommand{\experience}[4]{%
  \vspace{4pt}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}
  \vspace{-4pt}
}

\begin{document}

% ===== Header =====
\begin{center}
    {\Huge \textbf{JOANNE HOAR}} \\[4pt]
    {\Large \tech{Senior Software Developer}} \\[6pt]
    \faIcon{at}~\href{mailto:joanne.hoar@gmail.com}{joanne.hoar@gmail.com}
    \hfill
    \faIcon{phone}~+1\,403\,854\,8433
    \hfill
    \faIcon{linkedin}~\href{https://linkedin.com/in/joanne-hoar/}{linkedin.com/in/joanne-hoar}
    \hfill
    \faIcon{github}~\href{https://github.com/xcodegirl}{xcodegirl}~|~\href{https://github.com/jo-codegirl}{jo-codegirl}
    \hfill
    \faIcon{youtube}~\href{https://www.youtube.com/@linuxcodegirl/playlists}{youtube: linuxcodegirl}
    \\[2pt]
    \textit{Hanna, Alberta, Canada}~\textbullet~\textit{Remote}
\end{center}

% ===== Professional Summary =====
\section*{Summary}
Canadian Software Developer with 20 years of experience in video game programming, scientific modelling, and cross-platform development. Expertise in multiple programming languages, game engines, and SDKs. Proven track record in leading teams, mentoring developers, and building corporate culture. Strong background in C++, Unreal Engine, iOS, and Android using agile methodologies and CI/CD. Passion for algorithmic correctness, mathematics, artificial intelligence, and nature.

% ===== Core Competencies =====
\section*{Core Competencies}
\begin{multicols}{2}
\begin{itemize}
    \item C++, C\#, Objective-C, Swift, Kotlin
    \item Unreal Engine \& Game SDK Integration
    \item iOS \& Android Native Development
    \item Augmented Reality (ARKit) \& OpenGL Graphics
    \item CI/CD, TDD \& Agile Methodologies
    \item ASP .Net Core, React, Node.js, JavaScript
    \item Team Leadership \& Developer Mentorship
    \item Technical Curriculum Design
\end{itemize}
\end{multicols}

% ===== Professional Experience =====
\section*{Professional Experience}

\experience{Technology Instructor}{Jan 2025 -- Present}{Robertson College (contract) \normalfont\small\textit{--- Online Instructor-Guided}}{}
\begin{itemize}
    \item Instructed 20 course offerings across 12 subjects for \tech{Full Stack Development} and \tech{Data Analytics} diploma programs.
    \item Courses: C\# Programming, .NET, ASP .NET/Core, Object-oriented Programming (Java), Front End Frameworks, Intro to JavaScript, Web Development Basics, Data Collection, Testing \& QA, Version Control with Git \& GitHub, Introduction to IT.
    \item Deliver 3+ synchronous live sessions per week per course, including live coding and real-time student debugging.
    \item Maintain a GitHub repository of open-source course materials; archive session recordings for asynchronous access.
    \item Maintained average student satisfaction rating of \textbf{4.5/5.0} across evaluated courses; students cited approachability, real-world teaching style, and responsiveness.
    \item[] \tech{C\#, .NET, ASP .NET Core, Java, JavaScript, React, Git, GitHub, Azure, SQL, Testing \& QA}
\end{itemize}

\experience{Senior Software Developer}{2022 -- 2025}{bitHeads Inc. \normalfont\small\textit{--- brainCloud BaaS}}{}
\begin{itemize}
    \item Developed and maintained cross-platform client SDKs for \tech{brainCloud BaaS}, enabling gamification, leaderboards, matchmaking, lobbies, real-time multiplayer, and cloud code for \textbf{50+ published games} across \textbf{12 platforms} (PlayStation, Xbox, Nintendo Switch, Steam, iOS, Android, Oculus, and more).
    \item Primary focus: C++ client SDK, Unreal Engine plugin, iOS (Objective-C/Swift), Android Native (Java/Kotlin), and PlayStation; reviewed and debugged across all supported platforms and languages.
    \item Designed and built demonstration applications and widget libraries for every supported client platform — UI frameworks spanned \tech{Dear ImGui} (C++), Unreal Engine UMG, SwiftUI/UIKit (iOS), Android Views (Java/Kotlin), Unity (C\#), and PlayStation SDK.
    \item Built and maintained Unreal Engine sample projects (Space Shooter, Target Practice, Tappy Chicken, Relay Blast, dedicated server) to onboard client studios.
    \item Supported integration for notable titles including \textit{SUPERHOT VR}, \textit{Tony Hawk's Skate Jam}, \textit{Crypt of the NecroDancer}, and \textit{Invizimals} (PlayStation Mobile).
    \item Hired in part for educational background — role required teaching clients one-on-one, strong documentation skills, and developing academic examples and demonstrations.
    \item Engineered and maintained CI/CD and TDD pipelines; responded directly to customer issues and feature requests from AAA and Indie studio clients.
    \item[] \tech{Unreal Engine, C++, Objective-C, Swift, iOS, Android Native, Java, Kotlin, PlayStation, Nintendo Switch, Xbox, Node.js, Groovy, C\# (Unity, Godot), Shell Script, macOS, Windows, Linux}
\end{itemize}

\experience{Co-founder / Lead Developer / Instructor}{2005 -- 2022}{Silicon Hanna Inc. \normalfont\small\textit{(self-employed; founded as SuRJE Software Solutions Inc.; concurrent with BJ Pipeline 2005--08 and Fekete 2008--11)}}{}
\begin{itemize}
    \item Designed, coded, and published eleven games to commercial app stores for mobile devices across iOS and Android.
    \item Developed curriculum and instructed intermediate C++ programming for the \textbf{University of Calgary Department of Continuing Education}; received positive student feedback.
    \item Explored cutting-edge device technologies and SDKs including ARKit augmented reality, Chipmunk physics, and Unreal Engine.
    \item Technical writing, web development, Google Maps and Firebase integration, and server administration.
    \item[] \tech{Unreal Engine, Objective-C / Swift, iOS, Android Native, Kotlin, ARKit, C++, OpenGL, PHP, SQL, macOS, Windows, Linux}
\end{itemize}

\experience{Tools Programmer}{2008 -- 2011}{Fekete Associates Inc. (S\&P Global)}{}
\begin{itemize}
    \item Developed tools using mathematical models to maximize production and improve efficiency for major oil \& gas corporations.
    \item Contributed to the shared MFC-based UI tools library used as the consistent component foundation across all internal development projects.
    \item Led research on a new build system that reduced build times by 40\%.
    \item Designed and delivered a voluntary OpenGL elective for colleagues — presentations, sample code, and weekly assignments for both beginner and senior developers; received positive response from students and management.
    \item[] \tech{C++, MFC, Windows}
\end{itemize}

\experience{Intermediate Software Engineer}{2005 -- 2008}{BJ Pipeline Inspection Services Inc. (Baker Hughes)}{}
\begin{itemize}
    \item Visualized in-line inspection device data using OpenGL graphics for \tech{Vectra} and \tech{Gemini} 3D analysis products used by pipeline analysts and engineers.
    \item Implemented neural network algorithms for automated anomaly detection.
    \item Ported an Excel-based inspection reporting workflow to a full LAMP web application with interactive JavaScript forms, dynamic charts, and interactive geographic maps — replacing a static spreadsheet process with a live, accessible tool for non-technical stakeholders.
    \item Improved low-level C++ algorithms for high-performance data preprocessing.
    \item[] \tech{C++, C, OpenGL, PHP, JavaScript, SQL, Neural Networks, LAMP, Borland, Windows, Linux}
\end{itemize}

\newpage

\section*{Earlier Career Highlights}

\experience{Software Researcher / Lead Developer}{2005 -- 2006}{PlayStarMusic Corp. \normalfont\small\textit{(concurrent with BJ Pipeline)}}{}
\begin{itemize}
    \item Designed and built the end-user interface for a media streaming storefront — browsing, playback controls, purchase flow, and seamless DRM integration that kept the listening experience uninterrupted.
    \item Lead developer and system administrator for the full platform stack; developed a prototype for a competitive search engine.
    \item[] \tech{C++, PHP, JavaScript, .NET, Windows, Linux}
\end{itemize}

\experience{Junior Software Engineer}{2004 -- 2005}{Codefast.com}{}
\begin{itemize}
    \item Primary mandate: building graphical user interfaces for existing CLI tools — translating command-line workflows into accessible desktop applications.
    \item Ported applications across GUI libraries (Qt, Wx); developed user interfaces for software lifecycle automation tooling.
    \item[] \tech{C++, Qt, Wx, Shell Script, Windows, Unix}
\end{itemize}

\experience{Research Assistant}{2001 -- 2004}{VLab Computer Graphics Group / Artificial Intelligence Research Hub}{}
\begin{itemize}
    \item Developed graphics software tools using fractal mathematics and biological modelling.
    \item Managed network setup and code base for distributed computing infrastructure.
    \item Participated in interdepartmental projects and published five research papers.
    \item Served as teaching assistant for first-year and advanced third-year courses — supplemented instructor lesson plans with independent presentations and code/math walk-throughs.
    \item[] \tech{C++, OpenGL, Solaris, macOS, Unix, Linux, PHP, MySQL, Qt}
\end{itemize}

% ===== Education =====
\section*{Education}
\begin{itemize}
    \item \tech{M.Sc. Computer Science} -- University of Calgary \hfill 2004 \\
    \textit{Thesis: Agent-based Development of Natural Transportation Networks}
    \item \tech{B.Sc. Computer Science} -- University of Calgary \hfill 2001
\end{itemize}

% ===== Selected Publications =====
\section*{Selected Publications}
\begin{itemize}[nosep,leftmargin=*]
    \item Hoar, J., et al. ``Bacterial Chemotaxis in Silico,'' \textit{Australian Conference on Artificial Life (ACAL)}, 2003 \hfill \textit{Best Student Paper Award}
    \item Hoar, R., Jacob, C. ``The application of artificial intelligence to transportation system design,'' \textit{XRDS: Crossroads, ACM Magazine for Students}, 2003
\end{itemize}

% ===== Honors & Awards =====
\section*{Honors \& Awards}
\begin{itemize}[nosep,leftmargin=*]
    \item Departmental Nomination: Governor General's Gold Medal, Faculty of Graduate Studies \hfill 2005
    \item Postgraduate Scholarship NSERC D3, Natural Sciences and Engineering Research Council of Canada \hfill 2005
    \item Graduate Student Scholarship, Alberta Learning \hfill 2004
    \item Best Student Paper Award (Co-author), ACAL \hfill 2003
    \item CPSC Departmental Research Award, University of Calgary \hfill 2003
\end{itemize}

% ===== Published Games =====
\section*{Published Games}
\textit{Silicon Hanna Inc. (founded as SuRJE Software Solutions Inc.) --- 11 titles, 2008--2022:}
\begin{multicols}{2}
\begin{itemize}[nosep,leftmargin=*]
    \item Ragin' Bull -- iOS, Android (2020)
    \item AR Picture Portal -- iOS (2018)
    \item Fragment Reality -- iOS (2018)
    \item IceCream AR -- iOS (2018)
    \item Jewel Slide -- iOS, Android (2017, 2019)
    \item Word Slide \& Find -- iOS (2017)
    \item A Word Theme -- iOS, Android (2017, 2019)
    \item CryptoQuip -- iOS, Android (2011, 2019)
    \item Rafter's Loot -- iOS (2011)
    \item Star Chase -- iOS (2008)
    \item Bitsy -- iOS (2008)
\end{itemize}
\end{multicols}

% ===== Community Outreach & Leadership =====
\section*{Community Outreach \& Leadership}
\begin{itemize}[nosep,leftmargin=*]
    \item Treasurer, Hanna \& District Minor Soccer Association \hfill 2025--Present
    \item Vice President, Hanna Figure Skating Club \hfill 2024--Present
    \item Costume Coordinator, Stage Hanna Junior \hfill 2024
    \item Women of bitHeads and Cookbook Committee, bitHeads \hfill 2024
    \item Team Manager / Assistant Coach, U11 Soccer \hfill 2024
    \item Dryland Training Coordinator, Hanna Figure Skating Club \hfill 2022--2024
    \item 4-H Public Speaking Judge, District Level Competition \hfill 2022
    \item Computer Programming for Kids, J.C. Charyk School \hfill 2019--2021
    \item Reading Program, Our Lady of Fatima School \hfill 2016--2018
    \item Preschool Gym Leader, YMCA \hfill 2013--2014
    \item OpenGL Elective Instructor, Fekete Associates \hfill 2010
    \item Calgary Corporate Challenge \hfill 2007--2008
    \item Ladies Luncheon Club and Golf Tournament Coordinator, BJ Pipeline Inspection \hfill 2006--2008
    \item SCIberMENTOR Correspondent / Mentor \hfill 2002--2005
    \item President, Computer Science Graduate Society \hfill 2002--2003
    \item VP Academic, Computer Science Undergraduate Society \hfill 2001
\end{itemize}

% ===== Technical Skills =====
\section*{Technical Skills}
\textbf{Languages:} C++, C\#, JavaScript, Java, Objective-C, Swift, Kotlin, PHP, SQL \\
\textbf{Game \& Graphics:} Unreal Engine, OpenGL, ARKit, Augmented Reality, Real-time Multiplayer, Game SDK Integration \\
\textbf{Platforms \& Frameworks:} iOS, Android Native, ASP .Net Core, React, Node.js, Qt, MFC \\
\textbf{Tools \& Practices:} GitHub, Azure, CI/CD, TDD, Shell Script, Agile Methodologies \\
\textbf{Languages (Human):} English (native), French (intermediate), Spanish (rudimentary)

% ===== Work Samples =====
\section*{Work Samples}
\faIcon{github}~\href{https://github.com/xcodegirl/career/blob/main/xcodegirl-work-samples.md}{github.com/xcodegirl/career -- xcodegirl-work-samples.md}

\end{document}
