\documentclass[11pt]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage[default]{raleway}
\usepackage{multicol}

% Colors
\definecolor{accent}{RGB}{10,60,90}
\definecolor{secondary}{RGB}{30,30,30}

% Font settings
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\mytitle}[1]{\color{accent}\normalfont\large\bfseries{#1}}

% Section formatting
\titleformat{\section}{\mytitle}{}{0em}{}[{\titlerule[0.8pt]}]
\titlespacing{\section}{0pt}{12pt}{8pt}

% Itemize styling
\setlist[itemize]{leftmargin=*,nosep,after=\vspace{4pt}}
\setlist[itemize]{label=\color{accent}\scriptsize\raisebox{0.4ex}{\textbullet}}

% Custom commands
\newcommand{\tech}[1]{\textcolor{secondary}{\textbf{#1}}}

\newcommand{\experience}[4]{%
  \vspace{4pt}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}
  \vspace{-4pt}
}

\begin{document}

% ===== Header =====
\begin{center}
    {\Huge \textbf{JOANNE HOAR}} \\[4pt]
    {\Large \tech{Software Developer \& Technology Educator}} \\[6pt]
    \faIcon{at}~\href{mailto:joanne.hoar@gmail.com}{joanne.hoar@gmail.com}
    \hfill
    \faIcon{phone}~+1\,403\,854\,8433
    \hfill
    \faIcon{linkedin}~\href{https://linkedin.com/in/joanne-hoar/}{linkedin.com/in/joanne-hoar}
    \hfill
    \faIcon{github}~\href{https://github.com/xcodegirl}{xcodegirl}~|~\href{https://github.com/jo-codegirl}{jo-codegirl}
    \hfill
    \faIcon{youtube}~\href{https://www.youtube.com/@linuxcodegirl/playlists}{linuxcodegirl}
    \\[2pt]
    \textit{Hanna, Alberta, Canada}~\textbullet~\textit{Remote}
\end{center}

% ===== Professional Summary =====
\section*{Summary}
Canadian Software Developer and Technology Educator with a Master of Science in Computer Science (University of Calgary, including graduate-level HCI coursework) and over twenty years of continuous experience building user-facing systems. HCI has been the common thread across every role: translating CLIs into desktop GUIs at the start of a career, designing streaming media interfaces and interactive web applications mid-career, building cross-platform widget libraries and demo apps across seven UI frameworks at an SDK company, and now teaching front-end UI development to the next generation of developers online. Committed to accessible, student-centered teaching and to connecting HCI theory to real professional practice.

% ===== Core Competencies =====
\section*{Core Competencies}
\begin{multicols}{2}
\begin{itemize}
    \item HCI Principles \& Interaction Design
    \item Front-End UI Development (Angular, React)
    \item Game Interface Design \& Player Experience
    \item Augmented Reality (ARKit) \& 3D Graphics
    \item Accessibility \& Inclusive Design
    \item Online Course Delivery (Brightspace / D2L)
    \item Technical Curriculum Design \& Assessment
    \item Live Coding, Mentorship \& Student Feedback
\end{itemize}
\end{multicols}

% ===== Teaching Experience =====
\section*{Teaching Experience}

\experience{Technology Instructor}{Jan 2025 -- Present}{Robertson College (contract) \normalfont\small\textit{--- Online Instructor-Guided (Brightspace / D2L)}}{}
\begin{itemize}
    \item Deliver 20 course offerings across 12 subjects for \tech{Full Stack Development} and \tech{Data Analytics} diploma programs, including \textit{Front End Frameworks} (Angular \& React), \textit{Web Development Basics}, \textit{ASP.NET Core}, \textit{JavaScript}, \textit{C\# Programming}, \textit{Object-oriented Programming}, \textit{Version Control}, and more.
    \item Conduct 3+ synchronous live coding sessions per week; model real-time debugging and problem-solving to demystify professional practice.
    \item Design supplemental code examples, reference sheets, and video walkthroughs to support diverse learning styles; publish materials as open-source on GitHub.
    \item Earned average student satisfaction rating of \textbf{4.5/5.0}; feedback consistently highlights approachability, real-world teaching style, and responsiveness.
    \item[] \tech{Angular, React, ASP.NET Core, JavaScript, C\#, Java, Git, GitHub, Azure, SQL, Brightspace}
\end{itemize}

\experience{Research / Teaching Assistant}{2001 -- 2004}{VLab Computer Graphics Group / AI Research Hub, University of Calgary}{}
\begin{itemize}
    \item Served as TA for first-year introductory and advanced third-year computer science courses.
    \item Supplemented instructor lesson plans with independent presentations and code/math walk-throughs; received positive student feedback.
    \item Participated in interdepartmental research projects and contributed to five published papers.
    \item[] \tech{C++, OpenGL, PHP, Linux, Solaris}
\end{itemize}

% ===== HCI-Relevant Industry Experience =====
\section*{HCI-Relevant Industry Experience}

\experience{Senior Software Developer}{2022 -- 2025}{bitHeads Inc. \normalfont\small\textit{--- brainCloud BaaS}}{}
\begin{itemize}
    \item Designed and built demonstration applications and \textbf{widget libraries for every supported client platform} to showcase SDK capabilities --- a cross-platform UI portfolio spanning \tech{Dear ImGui} (C++), \tech{Unreal Engine UMG}, \tech{SwiftUI/UIKit} (iOS), \tech{Android Views} (Java/Kotlin), \tech{Unity} (C\#), and \tech{PlayStation SDK}.
    \item Maintained developer-facing APIs for 50+ published games across 12 platforms; API design requires the same HCI principles as any interface --- affordance, discoverability, error recovery, and minimal surprise.
    \item Authored onboarding documentation and sample projects engineered to minimize cognitive load for incoming client developers.
    \item Hired in part for educational background --- role required teaching clients one-on-one, strong documentation skills, and developing accessible examples and demonstrations.
    \item Supported integration for notable titles including \textit{SUPERHOT VR}, \textit{Tony Hawk's Skate Jam}, and \textit{Crypt of the NecroDancer} across 12 platforms.
    \item[] \tech{Unreal Engine, C++, iOS, Android, PlayStation, Nintendo Switch, Xbox, Node.js, C\# (Unity, Godot)}
\end{itemize}

\experience{Co-founder / Lead Developer / Instructor}{2005 -- 2022}{Silicon Hanna Inc. \normalfont\small\textit{(self-employed; founded as SuRJE Software Solutions Inc.; concurrent with BJ Pipeline 2005--08 and Fekete 2008--11)}}{}
\begin{itemize}
    \item Designed and shipped eleven mobile games; interaction design, touch interface usability, and player-experience feedback loops were central to every title.
    \item Developed augmented reality applications using \tech{ARKit}, designing novel spatial interfaces for consumer mobile devices.
    \item Instructed intermediate C++ programming for the \textbf{University of Calgary Department of Continuing Education}; developed curriculum, lectures, sample code, and assignments.
    \item[] \tech{Unreal Engine, Objective-C, Swift, iOS, Android, ARKit, Augmented Reality, C++}
\end{itemize}

\experience{Tools Programmer}{2008 -- 2011}{Fekete Associates Inc. (S\&P Global)}{}
\begin{itemize}
    \item Contributed to the company's shared \tech{MFC UI tools library} --- the consistent component foundation used across all internal development projects; brought UI coherence and interaction consistency to the full product suite.
    \item Built 3D data visualization tools (OpenGL) for pipeline analysis products; clarity of spatial information presentation was a direct safety concern.
    \item Designed and delivered a voluntary OpenGL graphics elective for colleagues; students built an interactive OpenGL widget within the MFC framework as a capstone project; adapted for both beginners and senior developers.
    \item[] \tech{C++, OpenGL, MFC, Windows}
\end{itemize}

\experience{Intermediate Software Engineer}{2005 -- 2008}{BJ Pipeline Inspection Services Inc. (Baker Hughes)}{}
\begin{itemize}
    \item Designed 3D OpenGL visualizations (\tech{Vectra}, \tech{Gemini}) for professional pipeline analysts; spatial data clarity was a safety-critical design requirement.
    \item Ported an Excel-based inspection reporting workflow to a full \tech{LAMP} web application with interactive JavaScript forms, dynamic charts, and interactive geographic maps --- replacing a static spreadsheet with a live, accessible tool for non-technical stakeholders.
    \item[] \tech{C++, OpenGL, PHP, JavaScript, SQL, LAMP}
\end{itemize}

\experience{Junior Software Engineer}{2004 -- 2005}{Codefast.com}{}
\begin{itemize}
    \item Primary mandate: build \textbf{graphical user interfaces for existing CLI tools} --- the definitive HCI task of making complex command-line workflows accessible to broader users.
    \item Ported applications across GUI frameworks (\tech{Qt}, \tech{Wx}); developed UIs for software lifecycle automation tooling.
    \item[] \tech{C++, Qt, Wx, Shell Script, Windows, Unix}
\end{itemize}

\experience{Software Researcher / Lead Developer}{2005 -- 2006}{PlayStarMusic Corp. \normalfont\small\textit{(concurrent with BJ Pipeline)}}{}
\begin{itemize}
    \item Designed the end-user interface for a media streaming storefront: browsing, playback controls, purchase flow, and seamless DRM integration that kept the listening experience uninterrupted.
    \item Lead developer and system administrator for the full platform stack.
    \item[] \tech{C++, PHP, JavaScript, .NET, Windows, Linux}
\end{itemize}

\newpage

% ===== Education =====
\section*{Education}
\begin{itemize}
    \item \tech{M.Sc. Computer Science} -- University of Calgary \hfill 2004 \\
    \textit{Thesis: Agent-based Development of Natural Transportation Networks} \\
    \textit{Graduate coursework included Human-Computer Interaction, Computer Graphics, and Artificial Intelligence}
    \item \tech{B.Sc. Computer Science} -- University of Calgary \hfill 2001
\end{itemize}

% ===== Selected Publications =====
\section*{Selected Publications}
\begin{itemize}[nosep,leftmargin=*]
    \item Hoar, J., et al. ``Bacterial Chemotaxis in Silico,'' \textit{Australian Conference on Artificial Life (ACAL)}, 2003 \hfill \textit{Best Student Paper Award}
    \item Hoar, R., Jacob, C. ``The application of artificial intelligence to transportation system design,'' \textit{XRDS: Crossroads, ACM Magazine for Students}, 2003
\end{itemize}

% ===== Honors & Awards =====
\section*{Honors \& Awards}
\begin{itemize}[nosep,leftmargin=*]
    \item Departmental Nomination: Governor General's Gold Medal, Faculty of Graduate Studies \hfill 2005
    \item Postgraduate Scholarship NSERC D3, Natural Sciences and Engineering Research Council of Canada \hfill 2005
    \item Graduate Student Scholarship, Alberta Learning \hfill 2004
    \item Best Student Paper Award (Co-author), ACAL \hfill 2003
    \item CPSC Departmental Research Award, University of Calgary \hfill 2003
\end{itemize}

% ===== Technical Skills =====
\section*{Technical Skills}
\textbf{HCI \& UI:} Interaction Design, User Experience, Accessible Design, Touch Interfaces, Augmented Reality, 3D Visualization, Front-End Frameworks \\
\textbf{Languages:} C++, C\#, JavaScript, TypeScript, Java, Objective-C, Swift, Kotlin, PHP, SQL \\
\textbf{Frameworks \& Tools:} Angular, React, ASP.NET Core, Unreal Engine, OpenGL, ARKit, Node.js, Azure, Git \\
\textbf{Teaching Tools:} Brightspace / D2L, GitHub (open-source course materials), Synchronous \& Asynchronous Online Delivery \\
\textbf{Platforms:} iOS, Android, macOS, Windows, Linux, PlayStation, Nintendo Switch, Xbox \\
\textbf{Languages (Human):} English (native), French (intermediate), Spanish (rudimentary)

% ===== Published Games =====
\section*{Published Interactive Applications}
\textit{Silicon Hanna Inc. (founded as SuRJE Software Solutions Inc.) --- 11 titles, 2008--2022:} Ragin' Bull, AR Picture Portal, Fragment Reality, IceCream AR, Jewel Slide, Word Slide \& Find, A Word Theme, CryptoQuip, Rafter's Loot, Star Chase, Bitsy

% ===== Community Outreach =====
\section*{Community Outreach \& Leadership}
\begin{itemize}[nosep,leftmargin=*]
    \item Computer Programming for Kids, J.C. Charyk School \hfill 2019--2021
    \item SCIberMENTOR Correspondent / Mentor \hfill 2002--2005
    \item President, Computer Science Graduate Society \hfill 2002--2003
    \item VP Academic, Computer Science Undergraduate Society \hfill 2001
    \item Treasurer, Hanna \& District Minor Soccer Association \hfill 2025--Present
    \item Vice President, Hanna Figure Skating Club \hfill 2024--Present
\end{itemize}

% ===== Work Samples =====
\section*{Work Samples}
\faIcon{github}~\href{https://github.com/xcodegirl/career/blob/main/xcodegirl-work-samples.md}{github.com/xcodegirl/career -- xcodegirl-work-samples.md}

\end{document}
